Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-05-28 manuscripts/manuscript.Rmd
use render instead of makefile

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville
abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question -- how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.
layout: preprint      # review, 11pt
output:
  pdf_document:
    keep_tex: true
    template: components/elsarticle.latex
    pandoc_args: [
      "--biblio", "components/references.bib",
      "--csl", "components/ecology.csl",
      "--metadata", "fontsize[:11]"
      ]
---

>>>>

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: 
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville
abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question -- how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.
layout: preprint      # review, 11pt
output:
  pdf_document:
    keep_tex: true
    template: components/elsarticle.latex
    pandoc_args: [
      "--biblio", "components/references.bib",
      "--csl", "components/ecology.csl",
      "--metadata", "fontsize[:11]"
      ]
---
